Path Model Temperature Comparisons

### 2016-07-18 path-temp-compare.Rmd
Add residual plots for remaining models.
I also had to revert to the 1.1.1 version of the 'piecewiseSEM' package because of an error about matrices mis-matching when I used the most recent version. The error arises in the 'sem.missing.paths' function I think, but that's where my investigating ended.

```{r load data, echo=F}
load("climate-path-model-data.RData")
library(piecewiseSEM); library(dplyr); library(lme4); library(lmerTest)

@@

```{r rescale variables, echo=F}
## rescale variables
# oakplots.sub2$inf_bay.scl <- scale((oakplots.sub2$infected_bay_ct))
oakplots.sub$tot_bay.scl <- scale(oakplots.sub$tot_bay)
oakplots.sub$tot_bay.log.scl <- scale(oakplots.sub$tot_bay.log)
oakplots.sub$umca_density_ha.scl <- scale(oakplots.sub$umca_density_ha)
oakplots.sub$umca_density_ha.log.scl <- scale(oakplots.sub$umca_density_ha.log)
oakplots.sub$umca_basal_area.scl <- scale(oakplots.sub$umca_basal_area)
oakplots.sub$umca_ba.log.scl <- scale(oakplots.sub$umca_ba.log)
oakplots.sub$tot_lfct.scl <- scale(oakplots.sub$tot_lfct)
oakplots.sub$tot_lfct.log.scl <- scale(oakplots.sub$tot_lfct.log)
# oakplots.sub$avg_lfct.scl <- scale(oakplots.sub$avg_lfct)
oakplots.sub$hrs_abv25ds.scl <- scale(oakplots.sub$hrs_abv25ds)
oakplots.sub$dys_abv25ds.scl <- scale(oakplots.sub$dys_abv25ds)
oakplots.sub$avg_tmax_ds.scl <- scale(oakplots.sub$avg_tmax_ds)
oakplots.sub$avg_hrsblw14_wet_tminus1.scl <- scale(oakplots.sub$avg_hrsblw14_wet_tminus1)
oakplots.sub$hrs1422_wet_tminus1.log.scl <- scale(oakplots.sub$hrs1422_wet_tminus1.log)
# oakplots.sub$avg_hrs1422_wet_t_t1.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1)
oakplots.sub$avg_hrs1422_wet_t_t1.log.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1.log)

## static variables
oakplots.sub$candens15m.scl <- scale(oakplots.sub$candens15m)
oakplots.sub$shannons2005.scl <- scale(oakplots.sub$H.2005)
oakplots.sub$shannons2014.scl <- scale(oakplots.sub$H.2014)
oakplots.sub$twi15m.scl <- scale(oakplots.sub$twi15m)
oakplots.sub$twi15m.log.scl <- scale(oakplots.sub$twi15m.log)
```

@@

      slc <- lmer(tot_lfct.log.scl ~ tot_bay.log.scl + hrs_abv25ds.scl + avg_hrs1422_wet_t_t1.log.scl + shannons2005.scl + twi15m.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

      umca_density <- lmer(umca_density_ha.log ~ twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

```{r symptomatic leaf count residuals plot}
plot(slc, main = "LMM of symptomatic leaf count residuals")
```

```{r wet-hours residuals plot}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year residuals")
```

```{r dry-season hours residuals plot}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season residuals")
```

```{r oak infection residuals plot}
plot(oak_infection, main = "Binomial GLMM of oak infection residuals")
```

@@

sem.fit(oak_and_bay_list1, oak_and_bay_plots, 
        corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log",
                        "tot_bay.log ~~ H.2005"))
```

@@

sem.coefs(oak_and_bay_list1, oak_and_bay_plots, standardize = "none",
          corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log",
                          "tot_bay.log ~~ H.2005"))
```

>>>>

```{r load data, echo=F}
load("climate-path-model-data.RData")
library(piecewiseSEM)# version 1.1.1, tried most recent version & kept getting errror 7/18/2016 b/c matrices rows were unequal in sem.missing.paths function
library(dplyr)
library(lme4)
library(lmerTest)

@@

```{r rescale variables, echo=F}
## rescale variables
# oakplots.sub2$inf_bay.scl <- scale((oakplots.sub2$infected_bay_ct))
oakplots.sub$tot_bay.scl <- as.numeric(scale(oakplots.sub$tot_bay))
oakplots.sub$tot_bay.log.scl <- as.numeric(scale(oakplots.sub$tot_bay.log))
oakplots.sub$umca_density_ha.scl <- as.numeric(scale(oakplots.sub$umca_density_ha))
oakplots.sub$umca_density_ha.log.scl <- as.numeric(scale(oakplots.sub$umca_density_ha.log))
oakplots.sub$umca_basal_area.scl <- as.numeric(scale(oakplots.sub$umca_basal_area))
oakplots.sub$umca_ba.log.scl <- as.numeric(scale(oakplots.sub$umca_ba.log))
oakplots.sub$tot_lfct.scl <- as.numeric(scale(oakplots.sub$tot_lfct))
oakplots.sub$tot_lfct.log.scl <- as.numeric(scale(oakplots.sub$tot_lfct.log))
# oakplots.sub$avg_lfct.scl <- scale(oakplots.sub$avg_lfct)
oakplots.sub$hrs_abv25ds.scl <- as.numeric(scale(oakplots.sub$hrs_abv25ds))
oakplots.sub$dys_abv25ds.scl <- as.numeric(scale(oakplots.sub$dys_abv25ds))
oakplots.sub$avg_tmax_ds.scl <- as.numeric(scale(oakplots.sub$avg_tmax_ds))
oakplots.sub$avg_hrsblw14_wet_tminus1.scl <- as.numeric(scale(oakplots.sub$avg_hrsblw14_wet_tminus1))
oakplots.sub$hrs1422_wet_tminus1.log.scl <- as.numeric(scale(oakplots.sub$hrs1422_wet_tminus1.log))
# oakplots.sub$avg_hrs1422_wet_t_t1.scl <- scale(oakplots.sub$avg_hrs1422_wet_t_t1)
oakplots.sub$avg_hrs1422_wet_t_t1.log.scl <- as.numeric(scale(oakplots.sub$avg_hrs1422_wet_t_t1.log))

## static variables
oakplots.sub$candens15m.scl <- as.numeric(scale(oakplots.sub$candens15m))
oakplots.sub$shannons2005.scl <- as.numeric(scale(oakplots.sub$H.2005))
oakplots.sub$shannons2014.scl <- as.numeric(scale(oakplots.sub$H.2014))
oakplots.sub$twi15m.scl <- as.numeric(scale(oakplots.sub$twi15m))
oakplots.sub$twi15m.log.scl <- as.numeric(scale(oakplots.sub$twi15m.log))
```

@@

      slc <- lmer(tot_lfct.log.scl ~ umca_density_ha.log.scl + hrs_abv25ds.scl + avg_hrs1422_wet_t_t1.log.scl + shannons2005.scl + twi15m.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

      wet_hours_1422 <- lmer(avg_hrs1422_wet_t_t1.log.scl ~ umca_density_ha.log.scl + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

      umca_density <- lmer(tot_bay.log ~ twi15m.log + (1|plotid) + (1|sample_year), data = oakplots.sub),

@@

```{r symptomatic leaf count residuals plot}
plot(slc, main = "LMM of symptomatic leaf count residuals")
plot(slc@frame$umca_density_ha.log, resid(slc),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "SLC model residuals vs. bay laurel density predictor")
plot(slc@frame$hrs_abv25ds, resid(slc),
     xlab = "# dry-season hours >25 C",
     ylab = "model residuals",
     main = "SLC model residuals vs. dry-season hours >25 C predictor")
plot(slc@frame$avg_hrs1422_wet_t_t1.log,
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "SLC model residuals vs. wet-hours predictor")
plot(slc@frame$H.2005, resid(slc),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "SLC model residuals vs. Shannon's diversity predictor")
plot(slc@frame$twi15m.log, resid(slc),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "SLC model residuals vs. wetness index predictor")
```

```{r wet-hours residuals plot}
plot(wet_hours_1422, main = "LMM of avg. # of hours 14-22 C current & prev. year residuals")
plot(wet_hours_1422@frame$umca_density_ha.log, resid(wet_hours_1422),
     xlab = "bay laurel density",
     ylab = "model residuals",
     main = "Wet-hours model residuals vs. bay laurel density predictor")
```

```{r dry-season hours residuals plot}
plot(hrs_abv25, main = "LMM of # of hours >25 C during prev. dry season residuals")
plot(hrs_abv25@frame$twi15m.log, resid(hrs_abv25),
     xlab = "wetness index",
     ylab = "model residuals",
     main = "Dry-season hours model residuals vs. wetness index predictor")
```

```{r oak infection residuals plot}
plot(oak_infection, main = "Binomial GLMM of oak infection residuals")
plot(oak_infection@frame$tot_lfct.log, resid(oak_infection),
     xlab = "symptomatic leaf count",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. symptomatic leaf count predictor")
plot(oak_infection@frame$avg_hrs1422_wet_t_t1.log, resid(oak_infection),
     xlab = "avg. wet-hours 14-22C",
     ylab = "model residuals",
     main = "Oak infectin model residuals vs. wet-hours predictor")
plot(oak_infection@frame$H.2005, resid(oak_infection),
     xlab = "Shannon's diversity index",
     ylab = "model residuals",
     main = "Oak infection model residuals vs. diversity predictor")
```

@@

# sem.fit(oak_and_bay_list1, oak_and_bay_plots, 
#         corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log",
#                         "tot_bay.log ~~ H.2005"))
```

@@

# sem.coefs(oak_and_bay_list1, oak_and_bay_plots, standardize = "none",
#           corr.errors = c("hrs_abv25ds ~~ avg_hrs1422_wet_t_t1.log",
#                           "tot_bay.log ~~ H.2005"))
```
